%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Yevhenii Budnyk}} & Email: \href{mailto:}{y.budnyk789@gmail.com}\\
  \href -Mobile:~~~+31 6 29137739\\
  \href{https://github.com/eugenumber1}{Github: ~~ https://github.com/Eugenumber1} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Twente}{Enschede, the Netherlands}
      {Bachelor of Science - Technical Computer Science;  GPA: 7.5}{September 2020 - November 2023 }
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Artificial Intelligence, Machine Learning, Cybersecurity, Software Systems, Network Systems, Databases, Data Science}}}
      \resumeSubheading
      {University of Twente Honors Program}{Enschede, the Netherlands}
      {Business and Entrepreneurship track;  available to the top 10\% of students}{February  2021 - July 2022 }
    \resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, Java, Perl, JavaScript, Haskell, C, C++}
	\resumeSubItem{Frameworks}{~~~~Scikit Learn, LangChain, Keras, PyTorch, FastAPI, Django, Selenium, React, NextJS}
	\resumeSubItem{Databases}{~~~PostgreSQL, SQLite, Pinecone, NeptuneDB, Neo4J}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~GIT, Docker, Figma, PyCharm, IntelliJ, Visual Studio Code}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Unix, Windows, Arduino, Raspberry, AWS, Rasa, Azure}
	\resumeSubItem{Soft Skills}{~~~~~~~Effective Communication, Leadership, Project Management, Team Collaboration, Problem Solving}

\resumeSubHeadingListEnd
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Accenture }{Amsterdam}
    {AI Software Engineer}{August 2024 - Present}
    \resumeItemListStart
    \resumeItem{Retrieval Augmented Generation}
          {Implemented an application using Natural Language Querying and Neo4j Graph Database, resulting in an 80\% reduction in diagram processing time.}
        \resumeItem{Customer Support Automation}
          {Designed an AI-powered customer support pipeline that integrated data from 5 sources, automating various administrative tasks and improving efficiency.}
        \resumeItem{User Satisfaction Enhancement}
          {Achieved a 2\% improvement in user satisfaction through LLM-generated text compared to human-written examples, validated in a randomized control trial.}
      \resumeItemListEnd
\vspace{-5pt}

    \resumeSubheading{LangWatch }{Amsterdam}
    {AI and Backend Developer}{March 2024 - August 2024}
    \resumeItemListStart
    \resumeItem{LLM Evaluator Automation}
          {Researched and developed LLM evaluators benefiting 4 clients, streamlining their evaluation processes.}
        \resumeItem{Custom Dashboard Development}
          {Built functionality for 3 custom analytics dashboards, enhancing user insights and data analysis.}
      \resumeItemListEnd
\vspace{-5pt}

    \resumeSubheading{AgencI }{Amsterdam}
    {Founder and Developer}{November 2023 - August 2024}
    \resumeItemListStart
    \resumeItem{Chatbot Development}
          {Designed and developed a stateful chatbot that automates waiter tasks, improving operational efficiency in restaurants.}
        \resumeItem{GenAI-Based System}
          {Built a CV and Cover Letter generation system utilizing GenAI with a Django backend framework.}
      \resumeItemListEnd
\vspace{-5pt}
    
    \resumeSubheading{Creative Mules }{Remote}
    {Full Stack Developer (Internship)}{August 2022 - February 2023}
    \resumeItemListStart
    \resumeItem{Automated Mood Board Creation}
          {Developed a full-stack prototype integrated with AWS services, enhancing design workflows for users.}
        \resumeItem{User Base Research}
          {Conducted 10 qualitative interviews to validate a product concept and gain insights into user needs.}
      \resumeItemListEnd
\vspace{-5pt}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Interactive chatbot for ZGT hospital (GPT3.5, LangChain, Rasa, Docker, Qdrant, React.js)}{(November 2023)}
    \resumeItemListStart
        \resumeItem{RAG Implementation}
          {Engineered a Retrieval Augmented Generation system that utilizes data from over 1000 PDF files for enhanced information retrieval.}
        \resumeItem{Chatbot Deployment}
          {Designed and co-developed a Rasa chatbot deployed in a Docker container, significantly improving user inquiry handling.}
        \resumeItem{Team Leadership}{Managed a team of 5 developers, effectively coordinating with stakeholders throughout the development process.}
	\resumeItemListEnd
\resumeSubItem{Research Project on Style Transfer in Lyrics Generation with Large Language Models}{(July 2023)}
\resumeItemListStart
        \resumeItem{Dataset Creation}
          {Created a curated version of a dataset containing 1,000,000 song lyrics, labeled using unsupervised techniques for improved analysis.}
        \resumeItem{Fine-tuning LLM - LyrAIX}
          {Optimized a pre-trained LLM neural network with 1.5 billion parameters, enhancing lyrical generation capabilities.}
	\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5pt}

\section{Extracurricular activities}
\resumeSubHeadingListStart
\resumeSubItem{CS Osvita Performance Engineering Course}{(September - December 2024)}
\resumeSubItem{ETHDam Hackathon 3rd Place}{(April 2024)}
\resumeSubItem{Negotiation Course at the University of Twente}{(September 2021 - July 2022)}
\resumeSubItem{BabyThings startup co-founder}{(February 2021 - July 2022)}
\resumeSubItem{Voice of Amsterdam startup co-founder}{(April 2021 - March 2022)}
\resumeSubItem{Twente Debating Society Secretary Board year (Secretary Position)}{(September 2020 - July 2021)}
\resumeSubHeadingListEnd
\vspace{-5pt}

\end{document}